Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex

%%What she said
The interviewee did shed some light onto why this change occurred. In order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented. An impact assessment was undertaken to determine if the removal of the function would be costly. Ultimately it was deemed appropriate and the function was removed from the API.

@@

%%Describe the change 
The case company included a selection of example programs to assist developers with creating applications. This trend continued in 2.0, but there were some significant improvements. The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.

%%Relate it to Categories
We therefore concluded that this change was updative as the example code was updated to the new API and the new techniques that it utilises. We further decided that this change also had a secondary category of reformative.

@@

%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API. Furthermore, the redesign would hopefully avoid future maintenance while allowing the system to be more extensible.

>>>>

%%What she said
The interviewee described that in order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented. An impact assessment was undertaken to determine if the removal of the function would be costly. Ultimately it was deemed appropriate and the function was removed from the API.

@@

%%Describe the change

The case company included a selection of example programs to assist developers with creating applications. This trend continued in 2.0, but there were some significant improvements. The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.

%%Relate it to Categories
We therefore concluded that this change was updative, as the example code was updated to the new API and the new techniques that it utilises. We further decided that this change also had a secondary category of reformative.

@@

%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API. Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended.
